Shaping the Perception of a Robot by Cognitive Priming

### 2016-01-26 main.tex
Shorten the title
new results
New results for some more statistical power and answers to a few
comments in the reviews

\rightheader{Shaping the Perception of a Robot by Cognitive Priming}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Shaping the Perception of a Robot as a Human-Like Agent by Cognitive
Priming}

@@

We evidence this effect with a novel methodology based on eye-tracking
and a set of stimuli that are visually identical and yet induce different
assumptions regarding the cognitive capabilities of the robot. By correlating
the resulting gaze patterns with answers to established questionnaires on
anthropomorphic attributions, we show that fixations on the head of the robot
indeed reflect how we perceive the machine.

Interestingly, we also show that humans appear quite sensitive to this effect:
even subtle context priming is sufficient to elicit significantly different
anthropomorphic attributions, and as such, this article provides new insights on
how our expectations of the robot's cognitive competency shape the bonds that we
build with the machine.

@@

Being such a central ingredient of the psychological ``sauce'' that binds humans to
robots, the field of human-robot interaction (HRI) has long~\fixme{ref?}
attempted to manipulate the anthropomorphic attributes we ascribe to robots.
While modifying the anthropomorphic \emph{design} of robots is conceptually
easy, influencing the underlying psychological phenomenon is less
obvious, although likely more effective.

One way consists in manipulating the context of use of the robot: when social,
entertaining or playful, it elicits more anthropomorphic attributions compared
routine or focused, serious situations (security, rescue, \etc).
\citet{joosse_what_2013} showed, for instance, that when the same robot (a {\sc
nao} humanoid) was used in a different task context (cleaning task \vs tour
guide), users would ascribe different personalities to the robot. Along the same
line, \citet{goetz_cooperation_2002} found that people prefer a serious robot
for serious tasks and a less serious robot for more playful tasks. Also related,
\citet{kaplan_free_2000} discussed how the uselessness of the robot impacts our
tendency to anthropomorphize it: artificial pets like AIBO have no real purpose,
in a sense that they do not provide any kind of service, and this very aspect
may increase people's tendency to anthropomorphize them.

We may hypothesize that these results are a consequence of different
expectations we form about the robot depending on the context: when a machine is
embedded in a social situation, for instance, we expect it to exhibit certain
social skills. However, the experiments conducted so far explore prototypical
opposite situations (routine \vs playful, typically boring \vs typically
intellectual): while they do confirm that the interaction context impacts our
perception of the robot, the stark contrast of the conditions makes it difficult
to finely analyse the psychological determinants that explain the different
perception of the robot.\fixme{references are needed} In particular, existing
techniques to measure anthropomorphism traditionally rely on questionnaires that
may suffer post-hoc reconstruction (we come back on this hereafter).

This article attempts to address this issue with a different experimental design
and a novel methodology to measure \emph{in-the-moment} anthropomorphic attributions.
Our approach is built on a combination of cognitive priming and eye-tracking,
and evidences specific gaze fixations on the head of the robot when the
participants are primed with higher expectations regarding the cognitive skills
of the robot.

@@

\textbf{TBD: Kshitij} at the end of this section, the reader must be convinced
that:
\begin{itemize}
    \item cognitive priming is a well established technique, grounded in the
        litterature,
    \item our terminology ('shallow' vs 'deep') is meaningful, and grounded
    \item our cognitive priming would impact the perception of the interaction
        situation as machine-like vs human-like (to support our manipulation
        check!)
\end{itemize}

@@

Assessing anthropomorphic attributions during a human-robot interaction is an
indirect mean to explore the intricate -- and dynamic -- bonds that build up
between the robot and its human partner. As such, a lot of literature in HRI has
investigated means of measuring anthropomorphism. This indeed raises interesting
methodological challenges, if only because of high inter-personal variations in
one's tendency to anthropomorphize~\fixme{ref?}, and the dynamic nature of
anthropomorphic attributions~\citep{lemaignan2014dynamics}.

One phenomenon requires particular attention: well established in the
psychological literature in terms of \emph{impulsive} or \emph{automatic} \vs
\emph{reflective} behaviours~\citep{strack2004reflective}, the way we behave and
perceive \emph{in-the-moment} is significantly different from what results from
a thoughtful (and slower) reflection on the situation. As noted by
\citet{takayama_perspectives_2012} for instance, this also impacts our
perspective on agency, and in fact, as shown by~\citet{nass_machines_2000}, in
the first phase of interaction with a robot, people might respond mindlessly,
and only after the so-called \emph{familiarization} period, one might respond in
a more conscious, reflective manner. The typical illustration of this mechanism
is found in~\citet{reeves_media_1996} who showed that participants who would
interact with technologies in ways similar to how they interact with people,
would however {\it a posteriori} typically deny having performed an human-like
interaction.

@@

\begin{inparaenum}[\itshape a\upshape)]
Two nested research questions have been presented so far: \item can we
characterize the link between expectations regarding the cognitive
skills of a robot and the effective ascription of anthropomorphic features to
this robot; and \item to this end, can we develop and validate a behavioural and
\emph{in-the-moment} metric of anthropomorphism?  \end{inparaenum}

@@

Secondly, we hypothesize that people with a higher tendency to anthropomorphize
robots will tend to look at robots and humans in similar ways, contrary to
people with a lower tendency to anthropomorphize (\h{2}). If this is verified,
it supports the idea that anthropomorphic attributions affect gaze patterns. The
hypothesis can be tested by correlating the participants' tendency to
anthropomorphize, measured from a standard questionnaire, with the comparative
gazing behaviour in two conditions (human task \vs robot task).

Third, we hypothesize that in the \emph{human-like} condition (higher ascription
of cognitive skills to the robot), the participants' gaze will be directed
significantly more towards the head of the robot than in the \emph{machine-like}
condition (low ascription of cognitive skills) (\h{3}). If verified, it
effectively means that the expectations held by the participants regarding the
cognitive capabilities of the robot are reflected by the eye fixations on the
head of the robot.  The hypothesis can be tested by comparing gaze fixations in
the two conditions (\emph{human-like} \vs \emph{machine-like}).

Finally, the hypothesis \h{4} proposes that manipulating cognitive expectations
affects the broader tendency to anthropomorphize robots, \ie whether observing one
robot acting in an \emph{human-like} context leads to an increased level of
anthropomorphic attributions to robots in general. The hypothesis can be
tested by looking at pre- and post-experiment self-reports on the tendency to
anthropomorphize.

If all these hypotheses are verified, the findings can be summarized as follow:
\h{1} shows that our manipulation (based on cognitive priming) does effectively
elicit lower or higher expectations in terms of the cognitive capabilities of
the robot; \h{4} shows that these expectations influence our tendency to
anthropomorphize robots; in parallel, \h{3} shows that these same expectations
shape the way we look at the robot by eliciting specific eye fixations on the
head of the robot; finally, \h{2} suggests that the fixation on the head
reflects human-likeliness and supports the thesis that head fixation can be used
as a behavioural measure of anthropomorphism.

@@

The study follows a 2$\times$2 design, summarized in table~\ref{table:design}.
Our two independent variables are the level of cognitive priming (\emph{shallow}
\vs \emph{deep}) and the nature of the agent appearing in the stimulus (a robot,
eliciting a \emph{human-robot} interaction situation, or a human, eliciting a
\emph{human-human} interaction situation).

@@

    \tikzmark{left}
    \begin{tabular}{l|p{4cm}|p{4cm}}
        & \tikzmark{top1} Shallow cognitive priming & Deep cognitive priming \tikzmark{top2}  \\
        \hline
        \tikzmark{left1} Robot & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''} \\
        \hline
        \tikzmark{left2} Human & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\ 
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''}\tikzmark{bottom} \\
        \end{tabular}

@@

Four different video stimuli where filmed (figure~\ref{fig:stimuli}): two
different tasks (picking a stuffed animal, refered hereafter as the
\emph{Picking} task, and pointing towards a source of sound, refered as the
\emph{Pointing} task) acted either by a human or a robot. Video stimuli were
realised in studio conditions. All videos followed the same simple structure: an
initial audio command (spoken by an invisible person), followed by the task
being executed.

The human actor was instructed to follow as closely as possible the actions and
attitudes of the robot (left/right glances, hesitations, gestures), while keeping a
natural, \emph{human-like} general behaviour. As a result, the length of human videos
(57 seconds in total for the two tasks) was shorter than robot videos (110
seconds) due to the robot being usually slower in performing actions (in
particular walks) compared to human.\footnote{To make sure the difference of
video lenght does not bias gaze distributions, we ran a $\chi^2$ test between
the gaze distributions of the first half and the second half of the robot
videos: no significant difference was found ($\chi^2[DF=4]=.0066, p=1$).}

The audio (and audio only) of these four videos was then edited to create two
sets of stimuli: one for the \emph{shallow cognitive priming} condition, one for
the \emph{deep cognitive priming} condition. The audio editing consisted in
inserting different commands to initiate the tasks (reported in
table~\ref{table:design}): in the \emph{Picking} task for instance, the object
that the agent had to pick was described either as a \emph{``brown toy''} or as
\emph{``your favorite toy''}. In the former case, the object was refered through
visible, objective features which do not suppose as deep cognitive capabilities
as in the latter case where the agent is implicitly supposed to have
tastes and preferences such as it can choose a toy as its favorite.

This simple verbal priming (\emph{``brown toy''} \vs \emph{``your favorite
toy''}) set the expectations regarding the cognitive capabilities of the robot
(\emph{shallow} \vs \emph{deep}) and was expected to lead to different
perceptions of the interaction (\emph{machine-like} \vs \emph{human-like}). We
reinforced this effect in the \emph{Pointing} task: not only the verbal priming
but also the sound played by the speakers during the task was altered: either a
repetitive bip (\emph{shallow cognitive priming}) or the sound of a crying baby
(\emph{deeper cognitive priming}).

@@

Before starting the experiment, the participants were asked to fill a
pre-questionnaire which had 49 questions (5-point Likert scale). The
questionnaire comprised of questions assessing their familiarity with robots, 10
items from the \emph{Big-Five} personality questionnaire, 15 questions taken from
Godspeed questionnaire (questions related to \emph{anthropomorphism},
\emph{likeability} and \emph{perceived intelligence}) and 20 questions rating
human-likeness (from~\cite{ruijten_introducing_2014})\footnote{The
pre- and post-questionnaires are available online:
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}. The pre-questionnaire
typically took 5 minutes for participants to fill. The results were turned into
a score noted \anti{} (\emph{initial tendency to anthropomorphize}) following a
method presented below (section~\ref{questionnaires_processing}).

@@

\subsubsection{Familiarization and Pre-questionnaire}

@@

We recorded the fixations on each of these zones and normalized them by
the full duration of the video stimulis and the surface of AOIs between the robot
and human conditions. We finally analyzed their distribution, producing what we call \emph{gaze
patterns}.

@@

\emph{Time} and \emph{Area} are normalized, respectively for the total
video length and the total area of the AOIs.

@@

Questionnaires were coded and two values, the \emph{initial tendency to
anthropomorphize} \anti{} and the \emph{final tendency to anthropomorphize} \antf{}
were computed, respectively from the pre- and post-questionnaires.

@@

\subsection{General Biases}

While testing for all the 4 hypotheses, we observed no significant bias with
respect to age, gender, familiarity with robot and robot ownership
of the participants, \ie there was no effects to be found between these factors
and the other variables of the experiment.

@@

\subsection{Impact of the Tendency to Anthropomorphize on Human
Gazing Behaviours}

We found a significant correlation between
$\delta_{\mathcal{H},\mathcal{R}}^{\text{gaze}}$ and
the \anti{}. As seen in figure~\ref{h2}, there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient $r(54) = -0.43,
p < .001$). The higher the (initial) tendency to anthropomorphize, the smaller
the difference in gazing behaviours between the robot and human conditions. This
supports hypothesis \h{2}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{H2}\label{GazeDifference-vs-ICA}
    \caption{Gaze distribution difference $\delta_{\mathcal{H},
    \mathcal{R}}^{\text{gaze}}$ \vs initial tendency to anthropomorphize \anti{}}
    \label{h2}
\end{figure}

@@

Running an ANOVA against the change of anthropomorphic attributions
(\deltaant) over the duration of the experiment in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($F(1,54) = 6.54, p <
.05$\fixme{put the exact p value here},
figure~\ref{h4}). In other words, after being exposed to short videos of a robot
performing simple tasks, participants primed with a deeper cognitive
expectations report a significantly higher tendency to anthropomorphize robots
\emph{in general} (as the questionnaire on anthropomorphic attributions
explicitly referred to \emph{robots in general}).

@@

The significant correlation between deep \vs shallow conditions and the
answers to the question \emph{Were the task more robot-like or human-like?}
shows that our manipulation was successful, and that a shallow cognitive
context was indeed associated to a robot-like situation, while a deeper
cognitive priming was associated to a human-like situation (\h{1}). This is
already an interesting result: subtle changes in the cognitive priming are
recognized and clearly interpreted in terms of human-likeness.

Hypothesis \h{2} looked at a possible interaction between our tendency to
anthropomorphize (as measured in the pre-questionnaire) and our actual gaze
behaviour, the hypothesis being that high anthropomorphizers would show smaller
differences between the way they look at robots and humans (since they would
consider robots closer to humans than low anthropomorphizers). Our data supports
this hypothesis: participants reporting an higher tendency to anthropomorphize
tend to have closer gazing behaviours when they look at humans or at robots:
statistically speaking, the tendency to anthropomorphize robots
is reflected in the way one looks at them: you look at them
like you would look at humans.

The third hypothesis \h{3} proposes that head fixations are related to the
cognitive expectations, which is clearly supported by our data: after deeper cognitive
priming, one tends to spend more time looking at the head of the interacting
agent than after shallow cognitive priming. We also hypothesized that, in turn,
head fixations could act as a \emph{proxy to anthropomorphic projections}: as
underlined in the previous section, our data also support this.

@@

The video stimuli had to obey to several constraints: they had to depict
plausible and legible situations, yet simple enough to be suitable for an
eye-tracking study (simple mechanics, easily distinguishable elements at
predictable locations). The body parts of the robot or human would need remain
visible most of the time. The actions had to be meaningful for both a robot and
a human, and both should be able to perform them in similar ways (similar pace,
similar movements) without looking ackward.

@@

This leads to a second-order effect that we also evidence here: depending on the
cognitive priming, the tendency to attribute human-like characteristics to robot
evolves in significantly different ways. After observing a robot in a
context that presupposes deeper cognitive capabilities, people increase
their general tendency to anthropomorphize robots compared to a shallow
cognitive priming, even though the robot appearance and visual behaviour is the
exact same.

@@

>>>>

\rightheader{Shaping the Perception of a Robot by Cognitive Priming}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Shaping the Perception of a Robot by Cognitive Priming}

@@

We show that humans appear quite sensitive to this effect:
even subtle context priming is sufficient to elicit significantly different
anthropomorphic attributions, and as such, this article provides new insights on
how our expectations of the robot's cognitive competency shape the bonds that we
build with the machine.

We evidence the effect with a novel methodology based on eye-tracking
and a set of stimuli that are visually identical and yet induce different
assumptions regarding the cognitive capabilities of the robot. By correlating
the resulting gaze patterns with answers to established questionnaires on
anthropomorphic attributions, we show that fixations on the head of the robot
indeed reflect how we anthropomorphize the machine.

@@

Being such a central ingredient of the psychological ``sauce'' that binds humans to
robots, the field of human-robot interaction (HRI) has long
attempted to manipulate the anthropomorphic attributes we ascribe to robots.
While modifying the anthropomorphic \emph{design} of robots is conceptually
easy, influencing the underlying psychological phenomenon is less
obvious, although possibly as effective.

One way consists in manipulating the context of use of the robot: when social,
entertaining or playful, it elicits more anthropomorphic attributions compared
routine or focused, serious situations (security, rescue, \etc).
\citet{joosse_what_2013} showed, for instance, that users would ascribe
different personalities to the same robot (a {\sc nao} humanoid) when it was
used in a different task context (cleaning task \vs tour guide). Along the same
line, \citet{goetz_cooperation_2002} found that people prefer a serious robot
for serious tasks and a less serious robot for more playful tasks. Also related,
\citet{kaplan_free_2000} discussed how the uselessness of the robot impacts our
tendency to anthropomorphise it: artificial pets like AIBO have no real purpose,
in a sense that they do not provide any kind of service, and this very aspect
may increase people's tendency to anthropomorphise them.

We may hypothesise that these results are a consequence of different
expectations we form about the robot depending on the context: when a machine is
embedded in a social situation, we expect it to exhibit certain
social skills. The experiments conducted so far only contrast prototypical
\emph{opposite} interaction situations (routine \vs playful, typically boring \vs typically
intellectual): while they do confirm that the interaction context impacts our
perception of the robot, the stark contrast of the conditions makes it difficult
to finely analyse the psychological determinants that explain the different
perception of the robot. In particular, existing
techniques to measure anthropomorphism traditionally rely on questionnaires that
may suffer post-hoc reconstruction (we further discuss this point hereafter).

This article attempts to address this issue with a different experimental design
and a novel methodology to measure \emph{in-the-moment} anthropomorphic attributions.
Our approach is built on a combination of cognitive priming and eye-tracking,
and evidences specific gaze fixations on the head of the robot when the
participants are primed with higher expectations regarding the cognitive skills
of the robot. This methodology leads us next to uncover and evidence the significant
impact of even subtle contextual cues on humans' tendency to ascribe human
traits to machines.

@@

\textbf{TBD: Kshitij} at the end of this section, the reader must be convinced
that:
\begin{itemize}
    \item cognitive priming is a well established technique, grounded in the
        literature,
    \item our terminology ('shallow' vs 'deep') is meaningful, and grounded
    \item our cognitive priming would impact the perception of the interaction
        situation as machine-like vs human-like (to support our manipulation
        check!)
\end{itemize}

@@

Assessing anthropomorphic attributions during a human-robot interaction is an
indirect mean to explore the intricate -- and dynamic -- bonds that build up
between the robot and its human partner. As such, a lot of literature in HRI has
investigated means of measuring anthropomorphism. This indeed raises interesting
methodological challenges, if only because of high inter-personal variations in
one's tendency to anthropomorphise~\fixme{ref?}, and the dynamic nature of
anthropomorphic attributions~\citep{lemaignan2014dynamics}.

One phenomenon requires particular attention: well established in the
psychological literature in terms of \emph{impulsive} or \emph{automatic} \vs
\emph{reflective} behaviours~\citep{strack2004reflective}, the way we behave and
perceive \emph{in-the-moment} is significantly different from what results from
a thoughtful (and slower) reflection on the situation. As noted by
\citet{takayama_perspectives_2012} for instance, this also impacts our
perspective on agency, and in fact, as shown by~\citet{nass_machines_2000}, in
the first phase of interaction with a robot, people might respond mindlessly,
and only after the so-called \emph{familiarisation} period, one might respond in
a more conscious, reflective manner. The typical illustration of this mechanism
is found in~\citet{reeves_media_1996} who showed that participants who would
interact with technologies in ways similar to how they interact with people,
would however {\it a posteriori} typically deny having performed an human-like
interaction.

@@

\begin{inparaenum}[\itshape a\upshape)]
Two nested research questions have been presented so far: \item can we
characterise the link between expectations regarding the cognitive
skills of a robot and the effective ascription of anthropomorphic features to
this robot; and \item to this end, can we develop and validate a behavioural and
\emph{in-the-moment} metric of anthropomorphism?  \end{inparaenum}

@@

Secondly, we hypothesise that people with a higher tendency to anthropomorphise
robots will tend to look at robots and humans in similar ways, contrary to
people with a lower tendency to anthropomorphise (\h{2}). If this is verified,
it supports the idea that anthropomorphic attributions affect gaze patterns. The
hypothesis can be tested by correlating the participants' tendency to
anthropomorphise, measured from a standard questionnaire, with the comparative
gazing behaviour in two conditions (human task \vs robot task).

Third, we hypothesise that in the \emph{human-like} condition (higher ascription
of cognitive skills to the robot), the participants' gaze will be directed
significantly more towards the head of the robot than in the \emph{machine-like}
condition (low ascription of cognitive skills) (\h{3}). If verified, it
effectively means that the expectations held by the participants regarding the
cognitive capabilities of the robot are reflected by the eye fixations on the
head of the robot.  The hypothesis can be tested by comparing gaze fixations in
the two conditions (\emph{human-like} \vs \emph{machine-like}).

Finally, the hypothesis \h{4} proposes that manipulating cognitive expectations
affects the broader tendency to anthropomorphise robots, \ie whether observing one
robot acting in an \emph{human-like} context leads to an increased level of
anthropomorphic attributions to robots in general. The hypothesis can be
tested by looking at pre- and post-experiment self-reports on the tendency to
anthropomorphise.

If all these hypotheses are verified, the findings can be summarised as follow:
\h{1} shows that our manipulation (based on cognitive priming) does effectively
elicit lower or higher expectations in terms of the cognitive capabilities of
the robot; \h{4} shows that these expectations influence our tendency to
anthropomorphise robots; in parallel, \h{3} shows that these same expectations
shape the way we look at the robot by eliciting specific eye fixations on the
head of the robot; finally, \h{2} suggests that the fixation on the head
reflects human-likeliness and supports the thesis that head fixation can be used
as a behavioural measure of anthropomorphism.

@@

The study follows a 2$\times$2 design, summarised in table~\ref{table:design}.
Our two independent variables are the level of cognitive priming (\emph{shallow}
\vs \emph{deep}) and the nature of the agent appearing in the stimulus (a robot,
eliciting a \emph{human-robot} interaction situation, or a human, eliciting a
\emph{human-human} interaction situation).

@@

    \tikzmark{left}
    \begin{tabular}{l|p{4cm}|p{4cm}}
        & \tikzmark{top1} Shallow cognitive priming & Deep cognitive priming \tikzmark{top2}  \\
        \hline
        \tikzmark{left1} Robot & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favourite toy''} \\
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''} \\
        \hline
        \tikzmark{left2} Human & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favourite toy''} \\ 
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''}\tikzmark{bottom} \\
        \end{tabular}

@@

Four different video stimuli where filmed (figure~\ref{fig:stimuli}): two
different tasks (picking a stuffed animal, referred hereafter as the
\emph{Picking} task, and pointing towards a source of sound, referred as the
\emph{Pointing} task) acted either by a human or a robot. Video stimuli were
realised in studio conditions. All videos followed the same simple structure: an
initial audio command (spoken by an invisible person), followed by the task
being executed.

The human actor was instructed to follow as closely as possible the actions and
attitudes of the robot (left/right glances, hesitations, gestures), while keeping a
natural, \emph{human-like} general behaviour. As a result, the length of human videos
(57 seconds in total for the two tasks) was shorter than robot videos (110
seconds) due to the robot being usually slower in performing actions (in
particular walks) compared to human.\footnote{To make sure the difference of
video length does not bias gaze distributions, we ran a $\chi^2$ test between
the gaze distributions of the first half and the second half of the robot
videos: no significant difference was found ($\chi^2[DF=4]=.0066, p=1$).}

The audio (and audio only) of these four videos was then edited to create two
sets of stimuli: one for the \emph{shallow cognitive priming} condition, one for
the \emph{deep cognitive priming} condition. The audio editing consisted in
inserting different commands to initiate the tasks (reported in
table~\ref{table:design}): in the \emph{Picking} task for instance, the object
that the agent had to pick was described either as a \emph{``brown toy''} or as
\emph{``your favourite toy''}. In the former case, the object was referred through
visible, objective features which do not suppose as deep cognitive capabilities
as in the latter case where the agent is implicitly supposed to have
tastes and preferences such as it can choose a toy as its favourite.

This simple verbal priming (\emph{``brown toy''} \vs \emph{``your favourite
toy''}) set the expectations regarding the cognitive capabilities of the robot
(\emph{shallow} \vs \emph{deep}) and was expected to lead to different
perceptions of the interaction (\emph{machine-like} \vs \emph{human-like}). We
reinforced this effect in the \emph{Pointing} task: not only the verbal priming
but also the sound played by the speakers during the task was altered: either a
repetitive bip (\emph{shallow cognitive priming}) or the sound of a crying baby
(\emph{deeper cognitive priming}).

@@

Before starting the experiment, the participants were asked to fill a
pre-questionnaire which had 49 questions (5-point Likert scale). The
questionnaire comprised of questions assessing their familiarity with robots, 10
items from the \emph{Big-Five} personality questionnaire, 15 questions taken from
Godspeed questionnaire (questions related to \emph{anthropomorphism},
\emph{likeability} and \emph{perceived intelligence}) and 20 questions rating
human-likeness (from~\cite{ruijten_introducing_2014})\footnote{The
pre- and post-questionnaires are available online:
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}. The pre-questionnaire
typically took 5 minutes for participants to fill. The results were turned into
a score noted \anti{} (\emph{initial tendency to anthropomorphise}) following a
method presented below (section~\ref{questionnaires_processing}).

@@

\subsubsection{Familiarisation and Pre-questionnaire}

@@

We recorded the fixations on each of these zones and normalised them by
the full duration of the video stimuli and the surface of AOIs between the robot
and human conditions. We finally analysed their distribution, producing what we call \emph{gaze
patterns}.

@@

\emph{Time} and \emph{Area} are normalised, respectively for the total
video length and the total area of the AOIs.

@@

Questionnaires were coded and two values, the \emph{initial tendency to
anthropomorphise} \anti{} and the \emph{final tendency to anthropomorphise} \antf{}
were computed, respectively from the pre- and post-questionnaires.

@@

%\subsection{General Biases}
First of all, we checked if there were any direct effects of the age, gender, familiarity with robot and robot ownership of the participants on the different aforementioned variables. We did not observe any such significant effects.

%While testing for all the 4 hypotheses, we observed no significant bias with
%respect to age, gender, familiarity with robot and robot ownership
%of the participants, \ie there was no effects to be found between these factors
%and the other variables of the experiment.

@@

\subsection{Impact of the Tendency to Anthropomorphise on Human
Gazing Behaviours}

We found a significant correlation between
$\delta_{\mathcal{H},\mathcal{R}}^{\text{gaze}}$ and
the \anti{}. As seen in figure~\ref{h2}, there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient $r(54) = -0.43,
p < .001$). The higher the (initial) tendency to anthropomorphise, the smaller
the difference in gazing behaviours between the robot and human conditions. This
supports hypothesis \h{2}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{H2}\label{GazeDifference-vs-ICA}
    \caption{Gaze distribution difference $\delta_{\mathcal{H},
    \mathcal{R}}^{\text{gaze}}$ \vs initial tendency to anthropomorphise \anti{}}
    \label{h2}
\end{figure}

@@

Running an ANOVA against the change of anthropomorphic attributions
(\deltaant) over the duration of the experiment in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($F(1,54) = 6.54, p <
.05$\fixme{put the exact p value here},
figure~\ref{h4}). In other words, after being exposed to short videos of a robot
performing simple tasks, participants primed with a deeper cognitive
expectations report a significantly higher tendency to anthropomorphise robots
\emph{in general} (as the questionnaire on anthropomorphic attributions
explicitly referred to \emph{robots in general}).

@@

The significant correlation between deep \vs shallow conditions and the
answers to the question \emph{Were the task more robot-like or human-like?}
shows that our manipulation was successful, and that a shallow cognitive
context was indeed associated to a robot-like situation, while a deeper
cognitive priming was associated to a human-like situation (\h{1}). This is
already an interesting result: subtle changes in the cognitive priming are
recognised and clearly interpreted in terms of human-likeness.

Hypothesis \h{2} looked at a possible interaction between our tendency to
anthropomorphise (as measured in the pre-questionnaire) and our actual gaze
behaviour, the hypothesis being that high anthropomorphisers would show smaller
differences between the way they look at robots and humans (since they would
consider robots closer to humans than low anthropomorphisers). Our data supports
this hypothesis: participants reporting an higher tendency to anthropomorphise
tend to have closer gazing behaviours when they look at humans or at robots:
statistically speaking, the tendency to anthropomorphise robots
is reflected in the way one looks at them: you look at them
like you would look at humans.

The third hypothesis \h{3} proposes that head fixations are related to the
cognitive expectations, which is clearly supported by our data: after deeper cognitive
priming, one tends to spend more time looking at the head of the interacting
agent than after shallow cognitive priming. We also hypothesised that, in turn,
head fixations could act as a \emph{proxy to anthropomorphic projections}: as
underlined in the previous section, our data also support this.

@@

The video stimuli had to obey to several constraints: they had to depict
plausible and legible situations, yet simple enough to be suitable for an
eye-tracking study (simple mechanics, easily distinguishable elements at
predictable locations). The body parts of the robot or human would need remain
visible most of the time. The actions had to be meaningful for both a robot and
a human, and both should be able to perform them in similar ways (similar pace,
similar movements) without looking awkward.

@@

This leads to a second-order effect that we also evidence here: depending on the
cognitive priming, the tendency to attribute human-like characteristics to robot
evolves in significantly different ways. After observing a robot in a
context that presupposes deeper cognitive capabilities, people increase
their general tendency to anthropomorphise robots compared to a shallow
cognitive priming, even though the robot appearance and visual behaviour is the
exact same.

@@

\newpage

\section {To be discussed}

% new results up for discussion on Skype
\subsection{Manipulation check - H1}

\begin{table}[ht]
\caption{Ordinal linear regression table for the manipulation check vs. cognitive context.}
\centering
\begin{tabular}{rrrrr}
  \hline
 & Value & Std. Error & t value & p value \\ 
  \hline
cond low & -2.52 & 0.57 & -4.39 & 0.00 \\ 
  -2$|$-1 & -4.06 & 0.66 & -6.19 & 0.00 \\ 
  -1$|$0 & -2.17 & 0.48 & -4.57 & 0.00 \\ 
  0$|$1 & -1.24 & 0.40 & -3.08 & 0.00 \\ 
  1$|$2 & 0.05 & 0.35 & 0.15 & 0.88 \\ 
   \hline
\end{tabular}
\end{table}

\subsection{Gaze difference vs. \anti levels- H2}

\begin{table}[ht]
\caption{\anti levels - high, low, neutral}
\centering
\begin{tabular}{rrrrr}
  \hline
 & diff & lwr & upr & p adj \\ 
  \hline
l-h & 0.10 & 0.02 & 0.18 & 0.01 \\ 
  n-h & 0.03 & -0.10 & 0.17 & 0.80 \\ 
  n-l & -0.06 & -0.18 & 0.06 & 0.44 \\ 
   \hline
\end{tabular}
\end{table}

\subsection{H3- the results remain the same}

One more result in deep (high) cognitive condition the participant stay on the head for longer periods,

We had a comment from the reviewers: 
`` In addition, you need to address that head fixations to the robot could increase because people are curious whether the robot really has the implied capacities, not because they assume it has them. Can you rule out this alternative interpretation?''

they leave other parts of body earlier and leave the head later this might reflect a hypothesis verification by the participants

\begin{table}[ht]
\caption{transition to and from ``head'' and Duration of looking at head}
\centering
\begin{tabular}{rrr}
  \hline
 & to & from \\ 
  \hline
high & 1441.075(-3.31) & 2646.870(2.62) \\ 
  low & 1882.956(3.14) & 2670.569(-2.48) \\ 
   \hline
\end{tabular}
\end{table}

MORE TO APPEAR``reported eye tracking results are far too cursory'' - I will put a nice factor analysis of the eye-tracking data with the questionnaire responses and then we can answer many questions in the results section.
